### 2016-07-07 lineups.Rnw
add file for calculating difference in parameter estimates.

<<est>>=
#For model $M_2$, parameter $\beta_3$ is estimated to be significantly different from zero in almost all cases \hh{(XXX how many exactly? XXX)}.

>>>>

<<est, echo = FALSE>>=
#For model $M_2$, parameter $\beta_3$ is estimated to be significantly different from zero in almost all cases \hh{(XXX how many exactly? XXX)}.
